Quanta concentration and Transmission risk

### 2024-11-22 analysis/simulation-results.Rmd
cleanup simulation results

```{r libraries}
library(tidyverse)
library(reshape2)
library(rstanarm)
library(tidybayes)
library(gganimate)

source("utils/plotting.r")
source("utils/tex.r")
source("models/stm-v2.R")

@@

## Main

### Quanta conc

```{r}
main_qc <- data.frame(
  files = list.files("simulations/main/",
    full.names = TRUE, pattern = "quanta_conc-.*.txt$",
    recursive = TRUE
  )
) %>%
  mutate(
    room = ifelse(grepl("Waiting", files), "Waiting room",
      ifelse(grepl("Corridor", files), "Corridor", "TB room")
    ),
    daytime = ifelse(grepl("morning", files), "morning", "afternoon")
  )

mean_qc <- function(file) {
  df <- read.table(file)
  colnames(df) <- c("sim", "x", "y", "value")
  df <- df %>%
    group_by(x, y) %>%
    summarize(value = mean(value)) %>%
    ungroup()
  return(df)
}

main_qc$value <- lapply(main_qc$files, mean_qc)

main_mean_qc <- main_qc %>%
  unnest(value) %>%
  group_by(room, daytime, x, y) %>%
  summarize(
    value = mean(value)
  ) %>%
  ungroup()

# example translation
source("utils/trans_risk.r")
IR_sit <- (.5 * IR("sitting", "male") + .5 * IR("sitting", "female")) / 3600
WR_vol <- convert_dist(cellSize)^2 * dimWR[3]
wr_morn <- main_mean_qc %>%
  filter(room == "Waiting room", daytime == "morning") %>%
  pull(value) %>%
  max()
wr_noon <- main_mean_qc %>%
  filter(room == "Waiting room", daytime == "afternoon") %>%
  pull(value) %>%
  max()
round((1 - exp(-wr_morn * 3600 * IR_sit / WR_vol)) * 100, 3)
round((1 - exp(-wr_noon * 3600 * IR_sit / WR_vol)) * 100, 3)

# link to building
main_mean_qc <- left_join(roomCoord,
  main_mean_qc %>% dplyr::select(room, daytime, x, y, value),
  by = c("x", "y", "room")
) %>%
  mutate(
    id = paste0("ID", id),
    daytime = factor(
      ifelse(daytime == "morning", "Morning", "Afternoon"),
      levels = c("Morning", "Afternoon")
    )
  )

# plot
mean_quanta_pl <- plot_spatial(
  ggplot(mapping = aes(x = long, y = lat, group = group, fill = value)) +
    facet_wrap(~daytime) +
    geom_polygon(
      data = left_join(
        fortify(waiting_room),
        filter(main_mean_qc, room == "Waiting room"),
        by = c("id")
      )
    ) +
    geom_polygon(
      data = left_join(
        fortify(corridor),
        filter(main_mean_qc, room == "Corridor"),
        by = c("id")
      )
    ) +
    geom_polygon(
      data = left_join(fortify(tb_room),
        filter(main_mean_qc, room == "TB room"),
        by = c("id")
      )
    ) +
    labs(
      fill = expression("Mean quanta concentration (quanta x 10"^-3 * " " * "m"^-3 * ")")
    ) +
    scale_fill_gradientn(
      colours = RColorBrewer::brewer.pal(n = 9, name = "YlOrRd"),
      labels = function(x) round(1e3 * x / (0.25^2 * 3), 1)
    ),
  8
) +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.key.height = unit(0.2, "cm"),
    legend.key.width = unit(1.5, "cm"),
    legend.title = element_text(margin = margin(r = 10))
  )

@@

### Trans risk

```{r}
average_trans_risk <- function(file) {
  average_tr <- read.table(file) %>%
    set_names(c("sim", "patient_id", "P")) %>%
    mutate(
      mthdy = stringi::stri_extract(file, regex = "\\d{2}-\\d{2}"),
      patient_id = paste(mthdy, patient_id, sep = "-")
    ) %>%
    group_by(patient_id) %>%
    summarize(
      P_mean = mean(P),
      P025 = quantile(P, .025),
      P975 = quantile(P, .975),
      P25 = quantile(P, .25),
      P75 = quantile(P, .75),
      P20 = quantile(P, .2),
      P80 = quantile(P, .8)
    ) %>%
    ungroup() %>%
    left_join(track %>%
      mutate(
        mth = lubridate::month(time),
        dy = lubridate::day(time)
      ) %>%
      group_by(patient_id, mth, dy) %>%
      slice(1) %>%
      ungroup() %>%
      mutate(dy = ifelse(nchar(dy) == 1, paste0("0", dy), dy)) %>%
      mutate(patient_id = paste(
        mth, dy,
        patient_id,
        sep = "-"
      )) %>%
      dplyr::select(patient_id, tracking_end)) %>%
    filter(tracking_end != "Possible HCW") %>%
    dplyr::select(-tracking_end) %>%
    mutate(
      P_col = ifelse(P_mean < .001, "Low",
        ifelse(P_mean < .01, "Medium", "High")
      ),
      P_col = factor(P_col, levels = c("Low", "Medium", "High"))
    )
  return(average_tr)
}

# average risk
main_tr <- data.frame(
  files = list.files("simulations/main/",
    full.names = TRUE, pattern = "trans-risk.txt$",
    recursive = TRUE
  )
)
main_tr$value <- lapply(main_tr$files, average_trans_risk)

@@

# annotation
annotate_average_trans_risk <- function(tr) {
  roi_annon <- tr %>%
    summarize(
      mean_P = mean(P_mean),
      lower_P = quantile(P_mean, .2),
      upper_P = quantile(P_mean, .8)
    ) %>%
    mutate(
      across(c(mean_P, lower_P, upper_P), ~ round_k(100 * .x, 2)),
      lab = paste0(
        mean_P, "%",
        " (80%-CrI ", lower_P, "% – ", upper_P, "%)"
      )
    )
  return(roi_annon)
}

main_annon <- annotate_average_trans_risk(main_tr)

main_annon
```

### Association

@@

```{r additional-analyses}
# files
files_nm <- list.files("simulations/nomasks/",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)
files_vent <- list.files("simulations/vent/",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)
files_nmvent <- list.files("simulations/nomasksvent/",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)

# average risk
nm_tr <- map_dfr(files_nm, average_trans_risk)
vent_tr <- map_dfr(files_vent, average_trans_risk)
nmvent_tr <- map_dfr(files_nmvent, average_trans_risk)

nm_tr %>%
  group_by(P_col) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  mutate(prop = round(n / sum(n) * 100, 0))

@@

main_tr %>%
  dplyr::select(patient_id, P_mean) %>%
  rename(`Spatiotemporal model` = P_mean) %>%
  left_join(
    nm_tr %>%
      dplyr::select(patient_id, P_mean) %>%
      rename(`No mask wearing` = P_mean)
  ) %>%
  left_join(
    vent_tr %>%
      dplyr::select(patient_id, P_mean) %>%
      rename(`Lower ventilation` = P_mean)
  ) %>%
  left_join(
    nmvent_tr %>%
      dplyr::select(patient_id, P_mean) %>%
      rename(`No mask wearing and lower ventilation` = P_mean)
  ) %>%
  mutate(
    mask_factor = `No mask wearing` / `Spatiotemporal model`,
    vent_factor = `Lower ventilation` / `Spatiotemporal model`,
    nmvent_factor = `No mask wearing and lower ventilation` / `Spatiotemporal model`
  ) %>%
  mean_qi(mask_factor, vent_factor, nmvent_factor) %>%
  gather() %>%
  head(9) %>%
  mutate(value = round(as.numeric(value), 1))

# combine
tr_comp <- rbind(
  main_tr %>% mutate(scenario = "a   Mask use and high ventilation"),
  nm_tr %>% mutate(scenario = "b   No mask use and high ventilation"),
  vent_tr %>% mutate(scenario = "c   Mask use and normal ventilation"),
  nmvent_tr %>% mutate(scenario = "d   No mask use and normal ventilation")
) %>%
  mutate(scenario = factor(scenario, levels = unique(scenario)))

# annotation
nm_annon <- annotate_average_trans_risk(nm_tr)
vent_annon <- annotate_average_trans_risk(vent_tr)
nmvent_annon <- annotate_average_trans_risk(nmvent_tr)

annon_comp <- rbind(
  main_annon %>% mutate(scenario = "a   Mask use and high ventilation"),
  nm_annon %>% mutate(scenario = "b   No mask use and high ventilation"),
  vent_annon %>% mutate(scenario = "c   Mask use and normal ventilation"),
  nmvent_annon %>% mutate(scenario = "d   No mask use and normal ventilation")
) %>%
  mutate(scenario = factor(scenario, levels = unique(scenario)))

# plot mean
mean_roi_comp_pl <- ggplot(
  tr_comp,
  aes(x = P_mean)
) +
  geom_histogram(
    mapping = aes(fill = P_col),
    binwidth = .0005,
    boundary = 1
  ) +
  geom_text(
    data = annon_comp,
    mapping = aes(x = Inf, y = Inf, label = lab),
    size = 8 / cm(1),
    hjust = 1, vjust = 2
  ) +
  facet_wrap(~scenario, ncol = 2, scales = "free_x") +
  scale_fill_manual(values = wes_palette("Darjeeling1")[c(2, 3, 1)]) +
  coord_cartesian(expand = FALSE) +
  scale_x_continuous(
    labels = function(x) x * 100,
    breaks = c(0, 0.001, 0.005, 0.01, 0.015, 0.02),
    limits = c(0, 0.02)
  ) +
  scale_y_sqrt(
    labels = scales::comma,
    breaks = c(0, 25, 100, 250, 500, 1000),
    limits = c(0, NA)
  ) +
  labs(
    x = "Risk of infection (%)",
    y = "Number of clinical attendees"
  ) +
  theme_custom() +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.key.height = unit(.6, "cm"),
    legend.key.width = unit(.4, "cm"),
    strip.text = element_text(hjust = 0),
    panel.spacing = unit(.5, "cm")
  )

@@

## Additional analysis

```{r} 
files_prev <- list.files("simulations/prevalence/",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)
files_susp <- list.files("simulations/suspected/",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)

prev_tr <- map_dfr(files_prev, average_trans_risk)
susp_tr <- map_dfr(files_susp, average_trans_risk)

tr_assum <- rbind(
  prev_tr %>% mutate(scenario = "a   Prevalence-based model"),
  susp_tr %>% mutate(scenario = "b   Suspected-based model")
) %>%
  mutate(scenario = factor(scenario, levels = unique(scenario)))

prev_annon <- annotate_average_trans_risk(prev_tr)
susp_annon <- annotate_average_trans_risk(susp_tr)

annon_assum <- rbind(
  prev_annon %>% mutate(scenario = "a   Prevalence-based model"),
  susp_annon %>% mutate(scenario = "b   Suspected-based model")
) %>%
  mutate(scenario = factor(scenario, levels = unique(scenario)))

# plot mean
mean_roi_assum_pl <- ggplot(
  tr_assum,
  aes(x = P_mean)
) +
  geom_histogram(
    mapping = aes(fill = P_col),
    binwidth = .0005,
    boundary = 1
  ) +
  geom_text(
    data = annon_assum,
    mapping = aes(x = Inf, y = Inf, label = lab),
    size = 8 / cm(1),
    hjust = 1, vjust = 2
  ) +
  facet_wrap(~scenario, ncol = 2) +
  scale_fill_manual(values = wes_palette("Darjeeling1")[c(2, 3, 1)]) +
  coord_cartesian(expand = FALSE) +
  scale_x_continuous(
    labels = function(x) x * 100,
    breaks = c(0, 0.001, 0.005, 0.01, 0.015, 0.02),
    limits = c(0, 0.02)
  ) +
  scale_y_sqrt(
    labels = scales::comma,
    breaks = c(0, 25, 100, 250, 500, 1000),
    limits = c(0, NA)
  ) +
  labs(
    x = "Risk of infection (%)",
    y = "Number of clinical attendees"
  ) +
  theme_custom() +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.key.height = unit(.6, "cm"),
    legend.key.width = unit(.4, "cm"),
    panel.spacing = unit(2, "cm"),
    strip.text = element_text(hjust = 0)
  )

>>>>

```{r libraries}
library(tidyverse)
library(parallel)
library(data.table)
library(reshape2)
library(betareg)
library(rstanarm)
library(tidybayes)
library(gganimate)

source("utils/plotting.r")
source("utils/tex.r")
source("models/stm-v2.R")
source("utils/trans_risk.r")

@@

## Quanta concentration

Show the average quanta concentration of the main simulation by daytime in the clinic 
and determine the corresponding transmission risk.

```{r}
# main quanta simulation files
main_qc <- data.frame(
  files = list.files("simulations/main",
    full.names = TRUE, pattern = "quanta_conc-.*.txt$",
    recursive = TRUE
  )
) %>%
  mutate(
    room = ifelse(grepl("Waiting", files), "Waiting room",
      ifelse(grepl("Corridor", files), "Corridor", "TB room")
    ),
    daytime = ifelse(grepl("morning", files), "morning", "afternoon")
  )

# read average quanta concentration by daytime, room and study day
read_quanta_table <- function(file, n_sim = 5000) {
  df <- data.table::fread(
    file,
    col.names = c("sim", "x", "y", "value")
  )
  n_origin <- nrow(df)
  df[, sim := as.integer(sim)]
  df[!sim %in% 1:n_sim, sim := NA]
  df <- na.omit(df)
  df <- df[, .SD[1], by = .(sim, x, y)]
  n_new <- nrow(df)

  if (n_origin > n_new) {
    warning(sprintf("File %s: %i defect rows removed", file, n_origin - n_new))
  }

  # check if simulations are complete
  sims <- unique(df$sim)
  missing_sims <- (1:n_sim)[!((1:n_sim) %in% sims)]
  n_missing <- length(missing_sims)
  if (n_missing > 0) {
    warning(sprintf("File %s: %i simulations missing.", file, n_missing))
  }

  return(df)
}

main_qc$data <- mclapply(main_qc$files, read_quanta_table, mc.cores = 15)

# compute daily mean quanta concentrations
main_qc$mean_conc <- lapply(main_qc$data, function(df) {
  df %>%
    group_by(x, y) %>%
    summarise(value = mean(value)) %>%
    ungroup()
})

# compte overall average quanta concentration
main_mean_qc <- main_qc %>%
  unnest(mean_conc) %>%
  group_by(room, daytime, x, y) %>%
  summarize(
    value = mean(value)
  ) %>%
  ungroup()

# corresponding transmission risk
ir_sit <- (.5 * IR("sitting", "male") + .5 * IR("sitting", "female")) / 3600
wr_vol <- (cellSize / 1e3)^2 * dimWR[3]
wr_morn <- main_mean_qc %>%
  filter(room == "Waiting room", daytime == "morning") %>%
  pull(value) %>%
  max()
wr_noon <- main_mean_qc %>%
  filter(room == "Waiting room", daytime == "afternoon") %>%
  pull(value) %>%
  max()
round((1 - exp(-wr_morn * 3600 * ir_sit / wr_vol)) * 100, 3)
round((1 - exp(-wr_noon * 3600 * ir_sit / wr_vol)) * 100, 3)

# link quanta concentration to building
main_mean_qc <- left_join(roomCoord,
  main_mean_qc %>% dplyr::select(room, daytime, x, y, value),
  by = c("x", "y", "room")
) %>%
  mutate(
    id = paste0("ID", id),
    daytime = factor(
      ifelse(daytime == "morning", "Morning", "Afternoon"),
      levels = c("Morning", "Afternoon")
    )
  )

# plot quanta concentration
mean_quanta_pl <- plot_spatial(
  ggplot(mapping = aes(x = long, y = lat, group = group, fill = value)) +
    facet_wrap(~daytime) +
    geom_polygon(
      data = left_join(
        fortify(waiting_room),
        filter(main_mean_qc, room == "Waiting room"),
        by = c("id")
      )
    ) +
    geom_polygon(
      data = left_join(
        fortify(corridor),
        filter(main_mean_qc, room == "Corridor"),
        by = c("id")
      )
    ) +
    geom_polygon(
      data = left_join(fortify(tb_room),
        filter(main_mean_qc, room == "TB room"),
        by = c("id")
      )
    ) +
    labs(
      fill = expression(
        "Mean quanta concentration (quanta x 10"^-3 * " " * "m"^-3 * ")"
      )
    ) +
    scale_fill_gradientn(
      colours = RColorBrewer::brewer.pal(n = 9, name = "YlOrRd"),
      labels = function(x) round(1e3 * x / (0.25^2 * 3), 1)
    ),
  8
) +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.key.height = unit(0.2, "cm"),
    legend.key.width = unit(1.5, "cm"),
    legend.title = element_text(margin = margin(r = 10))
  )

@@

## Transmission risk

Compute the patient-specific mean risk of infection 
and summarise the risk across patients for the main simulation.

```{r}
# main simulation files
main_tr <- data.frame(
  files = list.files("simulations/main",
    full.names = TRUE, pattern = "trans-risk.txt$",
    recursive = TRUE
  )
)

# read transmission risk data
read_risk_table <- function(file, n_sim = 5000) {
  # load data and remove duplicates
  df <- data.table::fread(
    file,
    select = 1:3,
    col.names = c("sim", "patient_id", "P"),
    fill = Inf
  )
  n_origin <- nrow(df)
  df[, sim := as.integer(sim)]
  df[!sim %in% 1:n_sim, sim := NA]
  df[, patient_id := as.integer(patient_id)]
  df[is.na(patient_id) | patient_id <= 0, patient_id := NA]
  df[, P := as.numeric(P)]
  df <- df[between(P, 0, 1)]
  df <- na.omit(df)
  df <- df[, .SD[1], by = .(sim, patient_id)]
  n_new <- nrow(df)

  if (n_origin > n_new) {
    warning(sprintf("File %s: %i defect rows removed", file, n_origin - n_new))
  }

  # check if simulations are complete
  sims <- unique(df$sim)
  missing_sims <- (1:n_sim)[!((1:n_sim) %in% sims)]
  n_missing <- length(missing_sims)
  if (n_missing > 0) {
    warning(sprintf("File %s: %i simulations missing.", file, n_missing))
  }

  # add unique mthdy and patient_id
  df <- df %>%
    mutate(
      mthdy = stringi::stri_extract(file, regex = "\\d{2}-\\d{2}"),
      patient_id = paste(mthdy, patient_id, sep = "-")
    )

  return(df)
}

main_tr$data <- lapply(main_tr$files, read_risk_table)

# compute mean risk per patient across simulations
patient_risk <- function(dat) {
  dat %>%
    group_by(patient_id) %>%
    summarize(
      P_mean = mean(P),
      P025 = quantile(P, .025),
      P975 = quantile(P, .975),
      P25 = quantile(P, .25),
      P75 = quantile(P, .75),
      P20 = quantile(P, .2),
      P80 = quantile(P, .8)
    ) %>%
    ungroup() %>%
    left_join(track %>%
      mutate(
        mth = lubridate::month(time),
        dy = lubridate::day(time)
      ) %>%
      group_by(patient_id, mth, dy) %>%
      slice(1) %>%
      ungroup() %>%
      mutate(dy = ifelse(nchar(dy) == 1, paste0("0", dy), dy)) %>%
      mutate(patient_id = paste(
        mth, dy,
        patient_id,
        sep = "-"
      )) %>%
      dplyr::select(patient_id, tracking_end)) %>%
    filter(tracking_end != "Possible HCW") %>%
    dplyr::select(-tracking_end) %>%
    mutate(
      P_col = ifelse(P_mean < .001, "Low",
        ifelse(P_mean < .01, "Medium", "High")
      ),
      P_col = factor(P_col, levels = c("Low", "Medium", "High"))
    )
}

main_tr$value <- lapply(main_tr$dat, patient_risk)

@@

# compute overall risk across patients
overall_risk <- function(tr) {
  roi_annon <- tr %>%
    summarize(
      mean_P = mean(P_mean),
      lower_P = quantile(P_mean, .2),
      upper_P = quantile(P_mean, .8)
    ) %>%
    mutate(
      across(c(mean_P, lower_P, upper_P), ~ round_k(100 * .x, 2)),
      lab = paste0(
        mean_P, "%",
        " (80%-CrI ", lower_P, "% – ", upper_P, "%)"
      )
    )
  return(roi_annon)
}

main_annon <- overall_risk(main_tr)
main_annon
```

## Association with patient risk factors

Estimate the association of the patient-specific risk of infection with 
time in clinic, number of close contacts, and time spent in close contact.

@@

Compare the modeled transmission risk with hypothetical scenarios 
to assess the effecs of implemented IPC measures (mask wearing and ventilation).

```{r additional-analyses}
# IPC scenario files
files_nm <- list.files("simulations/nomasks",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)
files_vent <- list.files("simulations/vent",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)
files_nmvent <- list.files("simulations/nomasksvent",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)

# mean risk per patient
nm_tr <- map_dfr(files_nm, function(f) patient_risk(read_risk_table(f)))
vent_tr <- map_dfr(files_vent, function(f) patient_risk(read_risk_table(f)))
nmvent_tr <- map_dfr(files_nmvent, function(f) patient_risk(read_risk_table(f)))

# overall risk
nm_annon <- overall_risk(nm_tr)
vent_annon <- overall_risk(vent_tr)
nmvent_annon <- overall_risk(nmvent_tr)
nm_annon
vent_annon
nmvent_annon

# patient risk by category
nm_tr %>%
  group_by(P_col) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  mutate(prop = round(n / sum(n) * 100, 0))

@@

# factor difference between scenarios
main_tr %>%
  dplyr::select(patient_id, P_mean) %>%
  rename(`Spatiotemporal model` = P_mean) %>%
  left_join(
    nm_tr %>%
      dplyr::select(patient_id, P_mean) %>%
      rename(`No mask wearing` = P_mean)
  ) %>%
  left_join(
    vent_tr %>%
      dplyr::select(patient_id, P_mean) %>%
      rename(`Lower ventilation` = P_mean)
  ) %>%
  left_join(
    nmvent_tr %>%
      dplyr::select(patient_id, P_mean) %>%
      rename(`No mask wearing and lower ventilation` = P_mean)
  ) %>%
  mutate(
    mask_factor = `No mask wearing` / `Spatiotemporal model`,
    vent_factor = `Lower ventilation` / `Spatiotemporal model`,
    nmvent_factor = `No mask wearing and lower ventilation` / `Spatiotemporal model`
  ) %>%
  mean_qi(mask_factor, vent_factor, nmvent_factor) %>%
  gather() %>%
  head(9) %>%
  mutate(value = round(as.numeric(value), 1))

# combine scenario-specific simulation results
tr_comp <- rbind(
  main_tr %>% dplyr::select(-data) %>%
    mutate(scenario = "a   Mask use and high ventilation"),
  nm_tr %>%
    mutate(scenario = "b   No mask use and high ventilation"),
  vent_tr %>%
    mutate(scenario = "c   Mask use and normal ventilation"),
  nmvent_tr %>%
    mutate(scenario = "d   No mask use and normal ventilation")
) %>%
  mutate(scenario = factor(scenario, levels = unique(scenario)))

# combine scenario-specific annotations (overall risk)
annon_comp <- rbind(
  main_annon %>% mutate(scenario = "a   Mask use and high ventilation"),
  nm_annon %>% mutate(scenario = "b   No mask use and high ventilation"),
  vent_annon %>% mutate(scenario = "c   Mask use and normal ventilation"),
  nmvent_annon %>% mutate(scenario = "d   No mask use and normal ventilation")
) %>%
  mutate(scenario = factor(scenario, levels = unique(scenario)))

# plot distribution with annotation
mean_roi_comp_pl <- ggplot(
  tr_comp,
  aes(x = P_mean)
) +
  geom_histogram(
    mapping = aes(fill = P_col),
    binwidth = .0005,
    boundary = 1
  ) +
  geom_text(
    data = annon_comp,
    mapping = aes(x = Inf, y = Inf, label = lab),
    size = 8 / cm(1),
    hjust = 1, vjust = 2
  ) +
  facet_wrap(~scenario, ncol = 2, scales = "free_x") +
  scale_fill_manual(values = wes_palette("Darjeeling1")[c(2, 3, 1)]) +
  coord_cartesian(expand = FALSE) +
  scale_x_continuous(
    labels = function(x) x * 100,
    breaks = c(0, 0.001, 0.005, 0.01, 0.015, 0.02),
    limits = c(0, 0.02)
  ) +
  scale_y_sqrt(
    labels = scales::comma,
    breaks = c(0, 25, 100, 250, 500, 1000),
    limits = c(0, NA)
  ) +
  labs(
    x = "Risk of infection (%)",
    y = "Number of clinical attendees"
  ) +
  theme_custom() +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.key.height = unit(.6, "cm"),
    legend.key.width = unit(.4, "cm"),
    strip.text = element_text(hjust = 0),
    panel.spacing = unit(.5, "cm")
  )

@@

## Prevalence comparison

Compare the modelled transmission risk with hypothetical scenarios 
to assess the impact of assumptions regarding TB prevalence (suspected patients, national prevalence).

```{r} 
# prevalence scenario files
files_prev <- list.files("simulations/prevalence",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)
files_susp <- list.files("simulations/suspected",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)

# mean risk per patient
prev_tr <- map_dfr(files_prev, function(f) patient_risk(read_risk_table(f)))
susp_tr <- map_dfr(files_susp, function(f) patient_risk(read_risk_table(f)))

# overall risk
prev_annon <- overall_risk(prev_tr)
susp_annon <- overall_risk(susp_tr)
prev_annon
susp_annon

# combine scenario-specific simulation results
tr_assum <- rbind(
  prev_tr %>% mutate(scenario = "a   Prevalence-based model"),
  susp_tr %>% mutate(scenario = "b   Suspected-based model")
) %>%
  mutate(scenario = factor(scenario, levels = unique(scenario)))

# combine scenario-specific annotations (overall risk)
annon_assum <- rbind(
  prev_annon %>% mutate(scenario = "a   Prevalence-based model"),
  susp_annon %>% mutate(scenario = "b   Suspected-based model")
) %>%
  mutate(scenario = factor(scenario, levels = unique(scenario)))

# plot distribution with annotations
mean_roi_assum_pl <- ggplot(
  tr_assum,
  aes(x = P_mean)
) +
  geom_histogram(
    mapping = aes(fill = P_col),
    binwidth = .0005,
    boundary = 1
  ) +
  geom_text(
    data = annon_assum,
    mapping = aes(x = Inf, y = Inf, label = lab),
    size = 8 / cm(1),
    hjust = 1, vjust = 2
  ) +
  facet_wrap(~scenario, ncol = 2) +
  scale_fill_manual(values = wes_palette("Darjeeling1")[c(2, 3, 1)]) +
  coord_cartesian(expand = FALSE) +
  scale_x_continuous(
    labels = function(x) x * 100,
    breaks = c(0, 0.001, 0.005, 0.01, 0.015, 0.02),
    limits = c(0, 0.02)
  ) +
  scale_y_sqrt(
    labels = scales::comma,
    breaks = c(0, 25, 100, 250, 500, 1000),
    limits = c(0, NA)
  ) +
  labs(
    x = "Risk of infection (%)",
    y = "Number of clinical attendees"
  ) +
  theme_custom() +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.key.height = unit(.6, "cm"),
    legend.key.width = unit(.4, "cm"),
    panel.spacing = unit(.5, "cm"),
    strip.text = element_text(hjust = 0)
  )
